Costs

### 2016-02-05 ms.tex
integrated results into remake workflow

%\begin{figure}[h!]
%\centering
%\includegraphics[width=10cm,height=10cm,keepaspectratio]{figures/example_costs}
%\caption{Example of escalating energy costs,}
%\label{fig:contests costs}
%\end{figure}

@@

@@

\begin{figure}[h!]
\centering
\includegraphics[width=15cm,height=15cm,keepaspectratio]{figures/area_searched}
\caption{the area searched by a male in interval $dt$}
\label{fig:area searched}
\end{figure}
\clearpage

>>>>

@@

\section{Results} % (fold)
\label{sec:results}

\begin{figure}[h!]
    \centering
    \includegraphics[width=15cm,height=10cm,keepaspectratio]{figures/energy_pc_plot.pdf}
    \caption{Percent energy expediture of cohort at generation 499}
    \label{fig:energy_pc}
\end{figure}

As patch area increases the number of fight oppurtunities decreases, 
This can probably explain the strong decrease in energy spent fighting. but I have no idea, early days yet.

\begin{figure}[h!]
    \centering
    \includegraphics[width=15cm,height=12cm,keepaspectratio]{figures/energy_total_plot.pdf}
    \caption{Total energy expeniture of cohort at generation 499}
    \label{fig:energy_total}
\end{figure}

\begin{figure}[h!]
    \centering
    \includegraphics[width=15cm,height=10cm,keepaspectratio]{figures/aggression_density.pdf}
    \caption{Number of successful males at different patch areas, gaps are because it took longer than 12 hours to run}
    \label{fig:num_winners}
\end{figure}

\begin{figure}[h!]
    \centering
    \includegraphics[width=15cm,height=10cm,keepaspectratio]{figures/num_winners.pdf}
    \caption{Number of successful males at different patch areas, gaps are because it took longer than 12 hours to run}
    \label{fig:num_winners}
\end{figure}

\clearpage
% section results (end)results

@@

\begin{figure}[h!]
\centering
\includegraphics[width=15cm,height=15cm,keepaspectratio]{figures/area_searched}
\caption{the area searched by a male in interval $dt$}
\label{fig:area searched figure}
\end{figure}
\clearpage

### 2016-02-05 scrap/aggression.Rmd
integrated results into remake workflow

k_min <- 0
k_max <- 2
e_0_min <- -2
e_0_max <- 2

@@

get_level_plotable <- function (e_current){
  old_aggression <- function(L, k, e_0){
    L / (1 + exp(-k*(e_current - e_0)))
  }
  k_val <- seq(k_min, k_max, by = 0.01)
  e_0_val <- seq(e_0_min, e_0_max, by = 0.01)
  r <- raster(outer(k_val, e_0_val, function(a, b){ old_aggression(L, a, b)}), 
              xmn = k_min,
              xmx = k_max,
              ymn = e_0_min,
              ymx = e_0_max)
  return(r)
}
my_theme <- BuRdTheme()

@@

levelplot(get_level_plotable(1), margin=FALSE, xlab = "K", ylab = "E_0", main = "Aggression", at = my_at, colorkey = my_ckey, par.settings=my_theme)

@@

```{R}
levelplot(get_level_plotable(0.5), margin=FALSE, xlab = "K", ylab = "E_0", main = "Aggression", at = my_at, colorkey = my_ckey, par.settings=my_theme)
```

@@

levelplot(get_level_plotable(0.1), margin=FALSE, xlab = "K", ylab = "E_0", main = "Aggression", at = my_at, colorkey = my_ckey, par.settings=my_theme)

>>>>

k_min <- -5
k_max <- 5
e_0_min <- -5
e_0_max <- 5

@@

get_level_plotable <- function (e_current){
  old_aggression <- function(L, k, e_0){
    L / (1 + exp(k*e_current + e_0))
  }
  k_val <- seq(k_min, k_max, by = 0.01)
  e_0_val <- seq(e_0_min, e_0_max, by = 0.01)
  r <- raster(outer(k_val, e_0_val, function(a, b){ old_aggression(L, a, b)}), 
              xmn = k_min,
              xmx = k_max,
              ymn = e_0_min,
              ymx = e_0_max)
  return(r)
}
my_theme <- BuRdTheme()

@@

levelplot(get_level_plotable(1), margin=FALSE, xlab = "K", ylab = "E_0", main = "Aggression, energy = 100%", at = my_at, colorkey = my_ckey, par.settings=my_theme)

@@

```{R}
levelplot(get_level_plotable(0.5), margin=FALSE, xlab = "K", ylab = "E_0", main = "Aggression, energy = 50%", at = my_at, colorkey = my_ckey, par.settings=my_theme)
```

@@

levelplot(get_level_plotable(0.1), margin=FALSE, xlab = "K", ylab = "E_0", main = "Aggression, energy = 10%", at = my_at, colorkey = my_ckey, par.settings=my_theme)

### 2016-02-05 scrap/costs.Rmd
integrated results into remake workflow

```{r}
library(rasterVis)
loser_masses <- seq(1, 100, by = 0.1)
winner_masses <- seq(1, 100, by = 0.1)
e_0 <- 0 
E_loser_max <- 100
cost_scaling <- 25

costs <- function( m_loser, m_winner){
    E_loser_max / (1 + exp(-((m_winner - m_loser)/cost_scaling - e_0)))
}

r <- raster(outer(loser_masses, winner_masses, costs), 
              xmn = 0,
              xmx = 100,
              ymn = 0,
              ymx = 100)
levelplot(r, margin = FALSE, 
          main = "Cost of Fighting", 
          xlab = "loser's mass",
          ylab = "winner's mass"
)
```

>>>>

```{r}
library(rasterVis)
loser_masses <- seq(1, 100, by = 0.1)
winner_masses <- seq(1, 100, by = 0.1)
e_0 <- 0 
E_loser_max <- 100

costs <- function( m_loser, m_winner, k){
    E_loser_max / (1 + exp(-((m_winner - m_loser) / k - e_0)))
}
```
costs_scaling <- 25:
```{R}
cost_scaling <- 25 # k 
r <- raster(outer(loser_masses, winner_masses, function(a,b){costs(a, b, cost_scaling)}), 
              xmn = 0,
              xmx = 100,
              ymn = 0,
              ymx = 100)

plot(r, 
  main = "Cost of Fighting k = 25", 
  xlab = "loser's mass",
  ylab = "winner's mass")
```

costs_scaling <- 50:
```{R}
costs_scaling <- 1
r <- raster(outer(loser_masses, winner_masses, function(a, b){costs(a, b, cost_scaling)}),
              xmn = 0,
              xmx = 100,
              ymn = 0,
              ymx = 100)

plot(r,
  main = "Cost of Fighting k = 1", 
  xlab = "loser's mass",
  ylab = "winner's mass")

```
